Incentivizing Exploration with Unbiased History

### 2018-10-29 llevel-overview.tex
update figures
llevel in intro

The main idea of extending from 3-level to $L$-level is that instead of using the second level as one ``check-point'', we use more levels to have multiple ``check points''.  Some new challenges appear in this process. Here give an overview of the additional techniques we use to get our $L$-level results.

@@

In order to avoid this undesirable factor, we design a slightly different connecting structure in our $L$-level policy. The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm $a$ when arm $a$'s mean is close enough to the best arm. However, it does not matter much if these agents see the same history of levels below $l-1$ because group sizes in lower levels are much smaller than group sizes in higher levels and the independent randomness in level $l-1$ is sufficient.

\xhdr{Additional groups for boundary cases.}

>>>>

The main idea of extending from 3-level to $L$-level is that instead of using the second level as one ``check-point'', we use more levels to have multiple ``check points''.  Some new challenges appear in this process. Here we give an overview of the additional techniques we use to get our $L$-level results.

@@

In order to avoid this undesirable factor, we design a slightly different connecting structure between levels in our $L$-level policy. The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm $a$ when arm $a$'s mean is close enough to the best arm. However, it does not matter much if these agents see the same history of levels below $l-1$ because group sizes in lower levels are much smaller than group sizes in higher levels and the independent randomness in level $l-1$ is sufficient.

For each level, we will have $S^2$ groups for some $S = \Theta(\log(T))$. The groups in the $l$-th level is labeled as $G_{l,u,v}$ for $u,v\in[S]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ sees the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level). This connecting structure has three nice properties: \\
(i) The number of groups does not grow with the level and stays as $S^2 = \Theta(\log^2(T))$.  Having these groups only adds a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(iii) For each set of groups in level $l-1$, agents in the level $l$ see the history of agents in one of these groups. Therefore, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
 }
\foreach \y in {2.5,5,7.5}
{
  \node at (12.5,\y+0.5){$\cdots$};
}

\foreach \y in {3.5,6}
{
  \draw (1,\y) -- (1,\y+1.5);
  \draw (1,\y) -- (7,\y+1.5);

  \draw (4,\y) -- (1,\y+1.5);
  \draw (4,\y) -- (7,\y+1.5);

  \draw (7,\y) -- (4,\y+1.5);
  \draw (7,\y) -- (10,\y+1.5);

  \draw (10,\y) -- (4,\y+1.5);
  \draw (10,\y) -- (10,\y+1.5);
}

\foreach \u in {1,2}
{
	\foreach \v in {1,2}
	{
	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
	\pgfmathsetmacro{\xa}{((\u-1))*3};
	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
   \node at(\x+1,8){$G_{l,\u,\v}$};
   \node at(\x+1,5.5){$G_{l-1,\u,\v}$};
   \node at(\x+1,3){$G_{l-2,\u,\v}$};
	}
}

  \node at(-1.2,3){\textbf{Level $l-2$}};
  \node at(-1.2,5.5){\textbf{Level $l-1$}};
  \node at(-1.2,8){\textbf{Level $l$}};
  \draw[->] (13.3,2)--(13.3,8.5);
  \node at(13.7,5)[ rotate=90]{Time};

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}
\xhdr{Additional groups for boundary cases.}
